---
title: "Day34--ChiSquareIV : Practice"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(openintro)
library(BSDA)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---
  
## Today's Agenda

+ Chi-Square tests can be used in three ways:
  - indpenedence of variables
  - goodness of fit
  - homogeneity
  
+ In every case you want to compute the chi-squared statistic:

$$\chi^2 = \sum \frac{(\text{observed}-\text{expected})^2}{\text{expected}}$$

+ In a goodness of fit test you KNOW the expected values. 
+ For example: 
  - is rolling a die uniform?
  - does a roulette table seem fair?
  - do your data match expectations from a population?
  
+ In a test of homogeneity you you don't exactly know the expected values, you need to calculate them. 
+ For example;
  - do North Carolinians and Californians have the same distribution of TVs in their homes (we don't know the distribution, we are just asking if the are similar)?
  - is distribution of amount of time spent on the computer per day the same between apple and android users? 
  
Compare and contrast the two questions:

Below is a table describing average amount of time spent on the computer in two groups:

| Avg. Hours per day | Group A | Group B |
|:--:|:--:|:--:|
| $<1$ hour | $30$ | $26$ | 
| $1-3$ hours | $35$ | $42$ | 
| $3-5$ hours | $25$ | $22$ | 
| $>5$ hours | $10$ | $10$ |
| Totals| | $100$ | $100$ |

1. If Group A is apple users and Group B is windows users, do the data provide evidence that the groups follow different distributions?

2. If Group A is apple users and Group B is the expected percentage in the entire population, do the data provide evidence that the group A does not follow the expected distribution?

## Correlation

For the following section we will use data from: "Learning Statistics with R" by Danielle Navarro:

```{r}
load("./parenthood.Rdata")
load("./pearson_correlations.RData")
load("./effort.Rdata")
```

+ This data captures how grumpy Danielle is, how much she slept in a day, and how much her baby slept in a day.

Consider the following plots:

```{r}
ggplot(parenthood, aes(x=dan.sleep, y=dan.grump)) + geom_point()
```

```{r}
ggplot(parenthood, aes(x=baby.sleep, y=dan.grump)) + geom_point()
```


## Correlation coefficient

The Pearson correlation coefficient $r_{XY}$ is a standardized covariance measure:

$$r_{XY} = \frac{1}{N-1} \sum_{i=1}^{N}
\frac{X_i-\bar{X}}{s_X}\frac{Y_i-\bar{Y}}{s_Y} $$

where $s_x$ and $s_y$ are the sample standard deviations. 

The R code for the Pearson correlation coefficient is:

### Properties of $r_{XY}$

### Interpreting the Pearson correlation coefficient

Below is data with various Pearson correlation coefficients:

```{r}
ggplot(outcomes, aes(x=V1,y=V2))+geom_point() + facet_wrap(~pearson)
```

+ Exactly what constitutes as a strong correlation depends on the context.
+ You can, however, use these general guidlines:

| Correlation | Strength | Direction |
|:--|:--|:--|
| $-1$ to $-0.9$ | Very Strong | Negative | 
| $-0.9$ to $-0.7$ | Strong | Negative | 
| $-0.7$ to $-0.4$ | Moderate | Negative | 
| $-0.4$ to $-0.2$ | Weak | Negative | 
| $-0.2$ to $0$ | Negligible | Negative | 
| $0$ to $0.2$ | Negligible | Positive | 
| $0.2$ to $0.4$ | Weak | Positive | 
| $0.4$ to $0.7$ | Moderate | Positive | 
| $0.7$ to $0.9$ | Strong | Positive | 
| $0.9$ to $1$ | Very Strong | Positive |

