---
title: "Day32--ChiSquareIII : Homogeneity"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(openintro)
library(BSDA)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---
  
## Today's Agenda
- Using Chi-Square table

---

1. Employers want to know which days of the week employees are absent in a five-day work week. Most employers would like to believe that employees are absent equally during the week. Suppose a random sample of $60$ managers were asked on which day of the week they had the highest number of employee absences. The results were distributed as:

|  | Monday | Tuesday | Wednesday | Thursday | Friday | Total |  
|:--:|:--:|:--:|:--:|:--:|
| number of absences | 15 | 12 | 9 | 9 | 15 | 60 |

Suppose there are $60$ absences in an average week. Test the goodness of fit of this data to a uniform distribution with a significance level of $.05$.



2. Suppose it is known that the distribution of males age $18$ to $24$ in the U.S. population is as follows:

| Marital Status | Percent | 
|:--:|:--:|
| never married | $31$ |
| married | $56.5$ | 
| widowed | $2.5$ |
|divorced/separated | $10$ | 

From a random sample of $400$ mean ages $18$ to $24$, the following data is collected:

| Marital Status | Count | 
|:--:|:--:|
| never married | $140$ |
| married | $238$ | 
| widowed | $2$ |
|divorced/separated | $20$ | 

Perform a goodness of fit test with significance level of $.05$.

```{r}

```

3. One study indicates that the number of televisions that American families have is distributed (this is the given distribution for the American population):

| Number of Televisions | Percent | 
|:--:|:--:|
| $0$ | $10$ |
| $1$ | $16$ | 
| $2$ | $55$ |
| $3$ | $11$ | 
| $4+$ | $8$ | 

A random sample of 600 families in North Carolina gave the following results:

| Number of Televisions | Count | 
|:--:|:--:|
| $0$ | $66$ |
| $1$ | $119$ | 
| $2$ | $340$ |
| $3$ | $60$ | 
| $4+$ | $15$ |

At the $1 \%$ significance level, does it appear that the distribution of number of televisions in North Carolina is different from the distribution for the American population as a whole?

```{r}

```

4. Suppose that $600$ thirty-year-olds were surveyed to determine whether or not there is a relationship between the highest education completed and salary. Conduct a test of independence. 

| Salary | No HS diploma | HS | College | Masters |
|:--:|:--:|:--:|:--:|:--:|:--:|:--:|
| $< \$30,000$ | $15$ | $25$ | $10$ | $5$ |
| $30$k$-40$k | $20$ | $40$ | $70$ | $30$ |
| $40$k$-50$k | $10$ | $20$ | $40$ | $55$ | 
| $50$k$-60$k | $5$ | $10$ | $20$ | $60$ |
| $> \$60,000$ | $0$ | $5$ | $10$ | $150$ |

$H_0:$  

$H_A:$

```{r}

```


## Correlation

For the following section we will use data from: "Learning Statistics with R" by Danielle Navarro:

```{r}
load("./parenthood.Rdata")
load("./pearson_correlations.RData")
load("./effort.Rdata")
```

+ This data captures how grumpy Danielle is, how much she slept in a day, and how much her baby slept in a day.

Consider the following plots:

```{r}
ggplot(parenthood, aes(x=dan.sleep, y=dan.grump)) + geom_point()
```

```{r}
ggplot(parenthood, aes(x=baby.sleep, y=dan.grump)) + geom_point()
```


## Correlation coefficient

The Pearson correlation coefficient $r_{XY}$ is a standardized covariance measure:

$$r_{XY} = \frac{1}{N-1} \sum_{i=1}^{N}
\frac{X_i-\bar{X}}{s_X}\frac{Y_i-\bar{Y}}{s_Y} $$

where $s_x$ and $s_y$ are the sample standard deviations. 

The R code for the Pearson correlation coefficient is:

### Properties of $r_{XY}$

### Interpreting the Pearson correlation coefficient

Below is data with various Pearson correlation coefficients:

```{r}
ggplot(outcomes, aes(x=V1,y=V2))+geom_point() + facet_wrap(~pearson)
```

+ Exactly what constitutes as a strong correlation depends on the context.
+ You can, however, use these general guidlines:

| Correlation | Strength | Direction |
|:--|:--|:--|
| $-1$ to $-0.9$ | Very Strong | Negative | 
| $-0.9$ to $-0.7$ | Strong | Negative | 
| $-0.7$ to $-0.4$ | Moderate | Negative | 
| $-0.4$ to $-0.2$ | Weak | Negative | 
| $-0.2$ to $0$ | Negligible | Negative | 
| $0$ to $0.2$ | Negligible | Positive | 
| $0.2$ to $0.4$ | Weak | Positive | 
| $0.4$ to $0.7$ | Moderate | Positive | 
| $0.7$ to $0.9$ | Strong | Positive | 
| $0.9$ to $1$ | Very Strong | Positive |