---
title: "CA 20 : Homogeneity"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(openintro)
library(BSDA)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---
  
## Today's Agenda
- Fitting a distribution
- chi-square independence
- Chi-square test of homogeneity

---

## Fitting a distribution... to another distribution

- The Chi-Squared statistic can also be used to test how well two distributions fit each other.

- The hypotheses are always:

$H_0$: the distributions are the same 

$H_A$: the distributions are different

+ The test progresses the exact same way as a test for independence; the expected values are computed with:

$$ \displaystyle  \frac{ (\text{row total} \cdot \text{column total})}{\text{table total}}$$

+ And the degrees of freedom is still 
$$df = (\# \text{of rows} - 1) \cdot (\# \text{of columns} - 1)$$

## Conditions 

+ All of the chi-squared tests require that all of the expected values are at least $5$.


#### Example: Do men and women college students have the same distribution of living arrangements? Use a level of significance of $0.05$. Suppose that $250$ randomly selected men college students and $300$ randomly selected women college students were asked about their living arrangements: dormitory, apartment, with parents, other. Do male and female college students have the same distribution of living arrangements?

|  | Dorm | Apartment | Parents | Other |
|:--:|:--:|:--:|:--:|:--:|:--:|:--:|
| Men | $72$ | $84$ | $49$ | $45$ |
| Women | $91$ | $86$ | $88$ | $35$ |

$H_0:$

$H_A:$




1. Ivy League schools receive many applications, but only some can be accepted. At the schools listed in below, two types of applications are accepted: regular and early decision.

| Type Accepted | Brown | Columbia | Cornell |
|:--:|:--:|:--:|:--:|:--:|:--:|:--:|
| Regular | $2115$ | $1792$ | $5306$ |
| Early Decision | $577$ | $627$ | $1228$ | 

At a $.05 \%$ significance level determine if the distributions are different.

```{r}

```


2. Employers want to know which days of the week employees are absent in a five-day work week. Most employers would like to believe that employees are absent equally during the week. Suppose a random sample of $60$ managers were asked on which day of the week they had the highest number of employee absences. The results were distributed as:

|  | Monday | Tuesday | Wednesday | Thursday | Friday | Total |  
|:--:|:--:|:--:|:--:|:--:|
| number of absences | 15 | 12 | 9 | 9 | 15 | 60 |

Suppose there are $60$ absences in an average week. Test the goodness of fit of this data to a uniform distribution with a significance level of $.05$.

3. Suppose it is known that the distribution of males age $18$ to $24$ in the U.S. population is as follows:

| Marital Status | Percent | 
|:--:|:--:|
| never married | $31.3$ |
| married | $56.1$ | 
| widowed | $2.5$ |
|divorced/separated | $10.1$ | 

From a random sample of $400$ mean ages $18$ to $24$, the following data is collected:

| Marital Status | Count | 
|:--:|:--:|
| never married | $140$ |
| married | $238$ | 
| widowed | $2$ |
|divorced/separated | $20$ | 

Perform a goodness of fit test with significance level of $.05$.

4. One study indicates that the number of televisions that American families have is distributed (this is the given distribution for the American population):

| Number of Televisions | Percent | 
|:--:|:--:|
| $0$ | $10$ |
| $1$ | $16$ | 
| $2$ | $55$ |
| $3$ | $11$ | 
| $4+$ | $8$ | 

A random sample of 600 families in North Carolina gave the following results:

| Number of Televisions | Count | 
|:--:|:--:|
| $0$ | $66$ |
| $1$ | $119$ | 
| $2$ | $340$ |
| $3$ | $60$ | 
| $4+$ | $15$ |

At the $1 \%$ significance level, does it appear that the distribution of number of televisions in North Carolina is different from the distribution for the American population as a whole?

```{r}

```

5. Suppose that $600$ thirty-year-olds were surveyed to determine whether or not there is a relationship between the highest education completed and salary. Conduct a test of independence. 

| Salary | No HS diploma | HS | College | Masters |
|:--:|:--:|:--:|:--:|:--:|:--:|:--:|
| $< \$30,000$ | $15$ | $25$ | $10$ | $5$ |
| $30$k$-40$k | $20$ | $40$ | $70$ | $30$ |
| $40$k$-50$k | $10$ | $20$ | $40$ | $55$ | 
| $50$k$-60$k | $5$ | $10$ | $20$ | $60$ |
| $> \$60,000$ | $0$ | $5$ | $10$ | $150$ |

$H_0:$  

$H_A:$

```{r}

```