---
title: "Day 17--Confidence Intervals I"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---

## Population Parameters aren't known

$$ \mu - 1.96 \cdot SE \leq \bar{X} \leq \mu + 1.96 \cdot SE $$

$$ \bar{X} - 1.96 \cdot SE \leq \mu \leq \bar{X} + 1.96 \cdot SE $$

+ This is for a 95% confidence level, where $\alpha=.05$. You can use any confidence level and only you will just need to change the 1.96 part.
+ The stuff that you add to either side is called the error bound. 

$$ \bar{X} - EB \leq \mu \leq \bar{X} + EB $$

1. Suppose a population unknown population mean and population standard deviation $2.5$. A sample of $450$ observations has a sample mean of $\bar{x}=62$. Find a $95 \%$ confidence interval.

```{r}

```

2. What are the $z$-scores corresponding to a $70 \%$ confidence level?

```{r}

```

3. A study is conducted to analyze internet privacy for teens. A group of $50$ teens is randomly sampled and $17$ report clicking on links from unknown email addresses. Construct a $90 \%$ confidence interval for the true proportion of teens that click on links from unknown email addresses.

```{r}

```

4. Suppose scores on exams in statistics are normally distributed with an unknown population mean and a population standard deviation of $3$ points. A random sample of $36$ scores is taken with an mean score of $72$. Find a $98 \%$ confidence interval for the mean exam score of the population.

```{r}

```

5. Political experts claim that only $35 \%$ of registered voters vote in local elections. A recent political poll (assume they are using methods that ensure independence) asks $1000$ registered voters if they plan to vote in their next local election. The poll finds that $840$ registered voters will vote in the next election. 

```{r}

```
