---
title: "Day 35--Linear Regression"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(car)
library(rgl)
library(palmerpenguins)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---

## Residuals

```{r}
load("./parenthood.Rdata")
load("./pearson_correlations.RData")
load("./effort.Rdata")
```

### Residuals

+ We can do better than estimating by eye though. 
+ We should choose the line that minimize the error in our predictions.

The graph below displays the error between our prediction and the true data in red:

```{r, eval=FALSE}
# Use our slope and intercept guesses to predict the y-values

predictions <- -12*parenthood$dan.sleep + 144

# Plot segments joining the actual points and the predicted points
ggplot(parenthood, aes(x=dan.sleep,y=dan.grump)) +
  geom_point() + 
  geom_abline(intercept = 144, slope = -12, color="blue") + 
  geom_segment(aes(xend = dan.sleep, yend = predictions, color = "residual"))
```

To lengths of these little red segments are called **residuals**. We can find how big the residuals are by finding the difference between the predicted value and the actual value:

$$\epsilon_i = Y_i - \hat{Y}_i$$

1. Calculate the residual corresponding to the first day, $\epsilon_1$. 
```{r}

```

+ the residual is **negative** when our prediction is an overestimate
+ the residual is **positive** when our prediction is an underestimate.

Putting these ideas together, we can see that our real data is equal to our prediction plus the residuals:

$$Y_i = \hat{Y}_i + \epsilon_i = b_1X_i + b_0 + \epsilon_i$$

---

## Minimizing error

+ One approach for this is to minimize the so called **sum of the squared residuals**:

$$ \sum \epsilon_i^2 = \sum (Y_i - \hat{Y}_i)^2$$

---

### Using R to find the fits


## Multiple Regression


The model we use for two predictors is:
$$\hat{Y}_i = b_2 X_{i,2} + b_1 X_{i,1} + b_0$$

where $X_{i,2}$ is the amount of sleep the baby got on day $i$ and $X_{i,1}$ is the amount of sleep Danielle got on day $i$.

+ If we had three predictors the equation would be:
$$\hat{Y}_i = b_3 X_{i,3} + b_2 X_{i,2} + b_1 X_{i,1} + b_0$$


To find the best fitting regression line we use `lm()`:

```{r,eval=FALSE}
scatter3d(dan.grump ~ dan.sleep + baby.sleep, parenthood)
rglwidget()
```

2. Find the residual corresponding to the first day using this new model with two predictors.

---

3. Using the penguins data set, perform a simple linear regression to model body mass using the predictor variable bill length. What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Graph a scatter plot for the data and include your regression model in the plot.

```{r}

```



$\hat{b}_0 =$

$\hat{b}_1 =$



4. Find the sum of the square residuals for the model in exercise 1.


5. Use `cor()` to find the strength of the correlation between bill length and body mass. 


```{r}

```



6. Use simple linear regression to model the relationship between flipper length and body mass for the penguin data. What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Plot a scatter plot for the data with the line you found.

```{r}

```

7. Use multiple linear regression to model the body mass using the predictors flipper length and bill length for the penguin data. Assuming $X_1$ is flipper length and $X_2$ is bill length, what values do you get for $\hat{b}_0$,  $\hat{b}_1$, and $\hat{b}_2$? 

```{r}

```

```{r}
# To find the line of best fit we use the lm() function:
```


```{r}
ggplot(parenthood, aes(x=dan.sleep,y=dan.grump)) +
  geom_point() 
```

So, our model is 


### Properties of the Linear Regression Model


```{r}
# show that (mean(x),mean(y)) is a point on the model

```

### Connections to the correlation $r_{XY}=R$

+ we can estimate the slope with the formula

$$b_1 = \frac{s_y}{s_x}R$$

```{r}
# compute the slope of the model with this shortcut

```


### Using R^2


8. Using the penguins data set, perform a simple linear regression to model body mass using the explanatory variable bill length. What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Graph a scatter plot for the data and include your regression model in the plot.

```{r}

```

$\hat{b}_0 =$

$\hat{b}_1 =$

9. Use `cor()` to find $R^2$ and compare this to what the linear model function `lm()` says it should be. 

```{r}

```

10. Use the formula for estimating $b_1$ in the penguin flipper length data and verify that it is the same value given by `lm()`.

```{r}

```

11. Use simple linear regression to model the relationship between flipper length and body mass for the penguin data. What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Plot a scatter plot for the data with the line you found.

```{r}

```


12. Use multiple linear regression to model the body mass using the explanatory variables flipper length and bill length for the penguin data. Assuming $X_1$ is flipper length and $X_2$ is bill length, what values do you get for $\hat{b}_0$,  $\hat{b}_1$, and $\hat{b}_2$? 

```{r}

```