---
title: "Day 37--Linear Regression II"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
library(palmerpenguins)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---

## Residuals

```{r}
load("./parenthood.Rdata")
load("./pearson_correlations.RData")
load("./effort.Rdata")
```

### Properties of the Linear Regression Model


```{r}
# show that (mean(x),mean(y)) is a point on the model

```

### Connections to the correlation $r_{XY}=R$

+ we can estimate the slope with the formula

$$b_1 = \frac{s_y}{s_x}R$$

```{r}
# compute the slope of the model with this shortcut

```


### Using R^2


1. Using the penguins data set, perform a simple linear regression to model body mass using the explanatory variable bill length (using the built in R function `lm()`). What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Graph a scatter plot for the data and include your regression model in the plot.

```{r}

```

$\hat{b}_0 =$

$\hat{b}_1 =$

2. Use `cor()` to find $R^2$ and compare this to what the linear model function `lm()` says it should be. 

```{r}

```

3. Use the formula for estimating $b_1$ in the penguin flipper length data and verify that it is the same value given by `lm()`.

```{r}

```

4. Use simple linear regression to model the relationship between flipper length and body mass for the penguin data. What values do you get for $\hat{b}_0$ and $\hat{b}_1$? Plot a scatter plot for the data with the line you found.

```{r}

```


5. Use multiple linear regression to model the body mass using the explanatory variables flipper length and bill length for the penguin data. Assuming $X_1$ is flipper length and $X_2$ is bill length, what values do you get for $\hat{b}_0$,  $\hat{b}_1$, and $\hat{b}_2$? 

```{r}

```