---
title: "Day3--Packages and Tables"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---
  
```{r global_options, include = FALSE}
library(knitr)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

---
  
## Today's Agenda
- Packages
- Tables

---


+ If you run the code it works
+ Now try to knit.

## Data frame basics


### Activities 

First thing we will do is install a new package. In the CONSOLE, run the appropriate code to install the package `fivethirtyeight`.

1. Load the `fivethirtyeight` package (which you should have just installed), locally

```{r}
# code to load the package

```

2. Inside this package is a dataset called `biopics` full of data about biographical picture movies. Choose a an appropriate name and save this data frame to your local environment.
```{r}
# saving data frame to environment

```


3. Try using the function `head()` on the data set. What does the `head()` function do?

```{r}
# See head() of biopic data

```

Type your answer in words here or write your answer as a comment in the code chunk

4. To read more about a particular data set you can use the help function. Run the code chunk below and explain what the column `box_office` in the data frame represents.

```{r}
# putting a ? at the beginning tells you more about the data
?biopics
```

Type your answer in words here or write your answer as a comment in the code chunk

5. How many movies are represented in the data frame? How many characteristics of each movie are recorded?

Type your answer to the question here

6. Classify the following variables as quantitative (discrete or continuous) or qualitative (nominal or ordinal).

+ `number_of_subjects`:
+ `type_of_subjects`:
+ `box_office`: 

7. Save the `number_of_subjects` column to your local environment.

```{r}
# saving number_of_subjects data locally

```

8. To see how many times each number of subject appears we can use the `table()` function.

```{r}
# use table() on the local variable you made in 7. 

```

9. Finally, try to run `barplot(table())` on the variable you made in 7.

```{r}
# use barplot(table()) on the local variable you made in 7. 

```

