---
title: "Day 14 Notes: Central Limit Theorem for Means"
output:
  html_document:
    css: ./style.css
    toc: yes
    toc_float: yes
    theme: cosmo
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r global_options, include = FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(eval = TRUE, results = TRUE)
```

------------------------------------------------------------------------

## Today's Agenda

- Law of Large Numbers
- Central Limit Theorem 

------------------------------------------------------------------------

## Law of Large Numbers

- Suppose you are trying to predict the proportion of Davidson students that plan to vote for Kamala Harris. 
- There is some true proportion (we don't know it)

- If we sample $400$ students, what is the expected value for the proportion of students voting for Harris?
- There are only two reasonable expectations to have:
  + we expect the sample proportion to be close to the true proportion
  + we expect the sample proportion to not be exactly equal to the true proportion
- how much are we likely to be wrong by? This is called the **standard error**
- the **standard error** is a measurement of how well we are able to predict some value. 
  + a large standard error means we cannot predict the value well
  + a small standard error means we can predict the value with high accuracy

- when we increase the sample size:
  + predicting the **number of people in the sample** voting for Harris gets harder (standard error for the number of people increases)
  + predicting the **percentage of people in our sample** voting for Harris gets easier (standard error for the proportion of people decreases)
  
```{r}
candidates <- c("H","T")
table(sample(candidates, 100, replace = TRUE))
```

## Central Limit Theorem

+ Let's investigate what happens to the sampling distribution of the sample mean as the sample size increases

```{r}
die <- c(1:6)
hist(die,breaks=20, prob=TRUE)
# what's the expected value of the mean of a die = 3.5
exp <- data.frame(means = replicate(100000,mean(sample(die,10,replace=TRUE))))
hist(exp$means,prob=TRUE,breaks=50)
```


